% Mini paper skeleton for MSR 2026 mining track.
% Compile: latexmk -pdf main.tex
\documentclass[sigconf,nonacm]{acmart}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}

\title{TerraDrift: An Empirical Study of Security Drift in Public Terraform Modules}

\author{Barrie20}
\affiliation{%
  \institution{[Your University]}
  \city{California}
  \country{USA}}
\email{your@email}

\begin{document}

\begin{abstract}
We present \textsc{TerraDrift}, the first empirical study of the
\emph{lifecycle} of security misconfigurations in public Terraform modules.
Mining $\sim$12{,}000 GitHub repositories and $\sim$4M commits, we measure
how long Checkov-classified CRITICAL/HIGH violations live in \texttt{main}
before being fixed and how often they regress after being patched. We
release the corpus, the analysis pipeline, and a 17-category taxonomy
linking Checkov rules to high-level CWE-aligned categories. Our preliminary
findings indicate that a substantial fraction of misconfigurations persist
for over six months, and a non-trivial fraction recur after fixes.
\end{abstract}

\maketitle

\section{Introduction}
Infrastructure-as-Code (IaC) has become the de-facto interface to public
cloud platforms. Yet little is known about the \emph{temporal} dynamics of
security misconfigurations in Terraform code at scale.

\section{Methodology}
We crawl public GitHub repositories containing \texttt{*.tf} files, applying
filters on activity and size. For each repository, we walk the full commit
history, run Checkov on each commit, and label the resulting findings using
our 17-category taxonomy. We then compute drift events between adjacent
commits.

\section{Findings (preliminary)}
\textbf{F1.} A non-trivial fraction of CRITICAL findings persist beyond
180 days. \textbf{F2.} Regression of previously-fixed findings is observed
in a non-trivial fraction of modules. \textbf{F3.} Modules with CI present
exhibit shorter median time-to-fix.

\section{Threats to Validity}
External validity is limited by the public-only sample. Construct validity
depends on Checkov rule stability; we report Checkov version explicitly.

\section{Artifact Availability}
Source code and the corpus manifest are available at
\url{https://github.com/Barrie20/terradrift}.

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}
